\documentclass[12pt]{article}
\usepackage[a4paper,left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{setspace}
\begin{document}
\doublespacing
\noindent
Cory Nezin\\
05/03/2018\\
HUM-335-1: Pythagoras
\begin{center}
\Large
The Mathematical Universe and Pythagoras
\end{center}

Pythagoras was the founder of the Pythagorean school and allegedly the first person to prove the so called Pythagorean theorem in generality.  While his work and life are shrouded in mystery, his name is ever present in mathematics and even the branch of philosophy known as metaphysics.  He is attributed the quote
\begin{quote}
\centering
``All things are number.''
\end{quote}
which has been the subject of many metaphysical studies.  Pythagoras seems quite an eccentric and even mythical figure.  He is the subject of many legends: He was said to be the son of Apollo, he had the ability to speak with animals, and of course he had a golden thigh.  The history of the Pythagorean school is almost just as mysterious.  The major limiting factor in the recording of Pythagorean history is that every single member had sworn an oath of silence.  This means that they could neither communicate the teachings of the school to the outside world, nor write it down for future historians to find.  

All of that being said, his dedication to mathematics is impressive.  In particular he is perhaps the first to realize that number is related to the physical universe in an extraordinary way.  His ideas regarding this were primitive, but revolutionary at the time.  His initial ideas have evolved and have been greatly refined over time, all the way to modern day.

I have chosen to write on the topic of a mathematical universe because I found it to be the most engaging topic during class dicsussion.  I have always been interested in mathematics, even pursuing a math minor at the cost of having to attend several 8:00 AM classes.  That last comment is mostly a joke.  I think my case is in this debate is unusual.  I had actually believed in a mathematical universe for most of high school and college.  After taking my high school physics class, I didn't even really realize there was an alternative option.  I now think it is a much harder question to answer.

My thesis is that at least since Pythagoras, the human treatment of the physical world has become increasingly mathematical.
\end{document}

